---
title: "Hotel_pricing In Indian Market"
author: "tavva_prudhvith"
date: "January 26, 2018"
output:
  word_document: default
  html_document: default
email: prudhvithtavva@gmail.com
COLLEGE: NIIT University
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The purpose of this project is to analyse the pricing strategy of hotels in the Indian hotel industry.
Many factors drive hotel room prices. The objective of this project is to identify the factors that matter the most. Think about the following problem:
Room Rent  = FUNCTION ( Date(s); Hotel Features; External Factors)


##Sumarize the data.
```{r hotel_pricing dataset}
hotel<-read.csv(file.choose(),header=T)
summary(hotel)
library(psych)
describe(hotel)
#Apply Some Functions
aggregate(hotel$RoomRent, by=list(freewifi = hotel$FreeWifi, freeBreakfast = hotel$FreeBreakfast, swimmingPool = hotel$HasSwimmingPool,Touristplace=hotel$IsTouristDestination), mean)

dim(hotel)
```

##One-Way Contingency Tables for categorial variables
```{r 1-way}
table1<-with(hotel,table(FreeWifi))
table1
prop.table(table1)*100 # Percentage For Free-Wifi
table2<-with(hotel,table(HasSwimmingPool))
table2
prop.table(table2)*100 #Percentage for Hotels which have swimming pools.
table3<-with(hotel,table(FreeBreakfast))
table3
prop.table(table3)*100 # Percentage For Free Breakfast
table4<-with(hotel,table(IsTouristDestination))
table4
prop.table(table4)*100 # Percentage For Hotels which is a Tourist Destination.
```

# Two-Way Contingency tables for categorial variables.  
```{r 2-way}
table5<-xtabs(~hotel$IsTouristDestination + hotel$IsWeekend)
table5
table6<-xtabs(~hotel$StarRating + hotel$IsMetroCity)
table6
table7<-xtabs(~hotel$StarRating + hotel$IsTouristDestination)
table7
```

## Boxplots For the variables present in 
```{r boxplots}
# Boxplot For Capacity.
boxplot(hotel$HotelCapacity,
    main="Boxplots for Hotel Capacity",
    col="blue",
    horizontal = T,
    xlab="Capacities")

#Boxplot for Room rent and Weekends.
boxplot(hotel$RoomRent ~ hotel$IsWeekend,
        horizontal=T,
        main="Room rent Vs IS weekend",
        xlab="Room Rents",
        ylab="Is Weekend",
col=c("pink","yellow"))

#Boxplots For Capacity and rating OF th Hotels.
boxplot(hotel$HotelCapacity ~ hotel$StarRating,
        horizontal=T,
        main="Hotel Capacity vs Star rating",
        xlab="Capacities",
        ylab="Ratings")

#boxplots FOr Hotel Capacity and Date.
boxplot(hotel$HotelCapacity~hotel$Date,
        main="Hotel Capacity vs. Date",
        ylab="Different Dates", 
        xlab="Room Rent rupees ",
        col=c("red","blue","green","yellow"),
        horizontal=TRUE)
```

## Histograms Of Suitable Data
```{r histograms}
# Histogram Of ratings For Hotels
hist(hotel$StarRating,
     main="Histogram Of Rating Of hotels",
     xlab="Ratings",
     breaks=10)

# Histograms for Distance Between Hotel to Airport.
hist(hotel$Airport,
     main="Histogram For  Distance From Hotel to Airport",
     xlab="Airport Distance in Km")

# Using Histogram command using lattice package to find the distributions of Date variable.
table(hotel$Date)
library(lattice)
histogram(~Date,data=hotel,
          main="Distribution Of Dates",
          xlab="Dates",
          col="yellow")

# Using Histogram command using lattice package to find the distributions of population variable.
histogram(~Population,
          data=hotel,
          main="Histogram For Distribution Of Populations",
          col="pink")
          
```


```{r  plots and barplots}
plot(hotel$RoomRent,
     hotel$Population,
     main="Rent VS Polulation",
     xlab="Rent",
     ylab="Population")

# Including the ones which have free wifi in hotels.
freewifi<-table(hotel$FreeWifi)
barplot(freewifi,
        main="barplot of having free wifi in the Hotel.")

#Including the ones which have free breakfast in the hotels.
breakfast<-table(hotel$FreeBreakfast)
barplot(breakfast,
        main="Boxplot Of having free breakfast in the hotel")

#Including the ones which have swimming pool in the hotels.
pool<-table(hotel$HasSwimmingPool)
barplot(pool,
        main="Boxplot Of having swimming Pool in the hotel")

```

Conclusion For the Above Plots and Barplots:
1.freewifi-According to the graph,there are more hotels having free wifi than the ones who doesn't have wifi.
2.breakfast-According to the graph,there are more hotels who give free breakfast than the ones who doesn't give breakfast.
3.pool-According to the graph,there are less number of hotels who have a swimming pool in their hotel.

```{r corrgram }
library(corrgram)
corrgram(hotel,main="Corrgram for the Attributes(columns)",
         lower.panel = panel.shade,
         upper.panel=panel.pie,
         order=T,
         text.panel = panel.txt)

#Let us find the Correlation Matrix For Rent,Pincode,airport and rating.

x<-hotel[,c("RoomRent","StarRating","Airport","FreeWifi")]
    
y<-hotel[,c("RoomRent","StarRating","Airport","FreeWifi")]
    cor(x,y)
    cov(x,y)
    var(x,y)
```
    
    
## Effect Of Star-Rating On Room rent.    
```{r }
library(car)
scatterplot(hotel$StarRating,hotel$RoomRent)
```


##Now,let us visualize the above correlation matrix with corrgram.
```{r}
library(corrgram)
    corrgram(hotel[,c("RoomRent","StarRating","Airport","FreeWifi")],
             order=T,
             lower.panel=panel.shade,
             upper.panel=panel.pie,
             text.panel=panel.txt)
```

Test1:-
Hypothesis:There is no significant difference between the Room Rent of Hotels providing free wifi and those which do not
```{r tests}

t.test(hotel$RoomRent ~ hotel$FreeWifi)
```
Result:As p-value is greater than 0.05 it suggests that there is no significant difference between the means of our Room rent and Free -Wifi.So,we could not reject null hypothesis.

Test2:-
Hypothesis:average Room rent hotels coming from tourist is more than people coming from cities.
```{r }
t.test(hotel$RoomRent,hotel$IsTouristDestination)
```
Result:As p-value is 2.2e-16 which is less than 0.05 suggests a significant difference between Room rent and Istouristdestination.So,We can reject Null Hypothesis.

Test3:-
Hypothesis:Average Room rent hotels having free breakfast is more than the hotels which doen't have any breakfast.
```{r}
t.test(hotel$RoomRent~hotel$FreeBreakfast)
```
Result:As p-value is greater than 0.05 it suggests that there is no significant difference between the means of our Room rent and free brerakfast.So,we could not reject null hypothesis.

Test4:-
Hypothesis:The Room Rents of Hotels on normal Eve are cheaper than that on New Year's Eve.
```{r }
t.test(RoomRent~IsNewYearEve,data=hotel)
```
result: As p-value is <0.05 ,it suggests that there is a significance differenc ebetween room rent hotels on normal eve and newyear eve.

Test5:-
Hypothesis:Room rent of hotels in non-metro cities are more expensive than hotels in metro cities.
```{r }
t.test(RoomRent~IsMetroCity,data=hotel)
```
result: As p-value is <0.05 ,it suggests that there is a significance differenc ebetween room rent hotels in metro cities and non-metro cities.

Test6:-
Hypothesis:Room rent of hotels having swimming pools are more expensive than hotels not having it.
```{r }
t.test(RoomRent~HasSwimmingPool,data=hotel)
```
Result:As p-value is <0.05 ,it suggests that there is a significance differenc ebetween room rent hotels having swimming pool and hotels that doesn't have swimming pool.

## Regression Models

## Regression Analysis(1)
```{r }
reg3<-lm(RoomRent~ StarRating +IsMetroCity +FreeBreakfast,data=hotel)
summary(reg3)

reg3$coefficients
```
As Y=F(x) 
y=Room Rent
x1,x2,x3,... are exploratory variables dependnt upon the room rent i.e the factors.
Room rent =b0 +b1 *Starrating + b2*ismetrocity +b3*freebreakfast
From the fitted coefficients,then 
b0=-1 (let us assume)
b1=3656.730
b2=-1568.661
b3=113.012
The Conclusion will be 
Room rent =(-1) +3517.46 *Starrating + (-1568.661)*ismetrocity +113.012*freebrreakfast


# Regression Analysis (2) 
```{r }
reg1<-lm(RoomRent~StarRating + Airport + HasSwimmingPool + HotelCapacity + FreeWifi,data=hotel)
summary(reg1)

reg1$coefficients
```

As Y=F(x) 
y=Room Rent
x1,x2,x3,... are exploratory variables dependnt upon the room rent i.e the factors.
Room rent =b0 +b1 *Starrating + b2*airport +b3*hasswimmingpool +b4*hotelcapacity
From the fitted coefficients,then 
b0=-1 (let us assume)
b1=3517.45652 
b2=25.59515 
b3=2716.24231
b4=-14.75071
The Conclusion will be 
Room rent =(-1) +3517.46 *Starrating + 25.6*airport +2716.24*hasswimmingpool +(-14.75)*hotelcapacity


## Regression Analysis (3)
```{r }
reg2<-lm(RoomRent ~ StarRating + Airport + HotelCapacity + IsWeekend + HasSwimmingPool,data=hotel)
summary(reg2)

reg2$coefficients
```

As Y=F(x) 
y=Room Rent
x1,x2,x3,... are exploratory variables dependnt upon the room rent i.e the factors.
Room rent =b0 +b1 *Starrating + b2*airport +b3*hotelcapacity +b4*isweekend +b5*hasswimmingpool
From the fitted coefficients,then 
b0=-1 (let us assume)
b1=3522.88515
b2=25.34555
b3=-14.77651
b4=40.17697
b5=2708.40430
The Conclusion will be 
Room rent =(-1) +3522.89 *Starrating + 25.34*airport + (-14.8)*hotelcapacity + 40.17*isweekend + 2708.4*hasswimmingpool.


















